P.berghei pir analysis

### 2021-08-31 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_Github_Pberghei_pir.Rmd
Change from counts.xlsx to .csv

---
title: "P.berghei pir analysis"
author: "Timothy Little"
date: "12/03/2021"
output: 
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = TRUE, message = FALSE, warning = FALSE)
# Set below to your own working directory.
knitr::opts_knit$set(root.dir = 
                       ".")
options(scipen = 999) # Means that numbers are displayed normally not as 1e6 (1000000)
```

@@

```{r read_files}
#Reading in the counts from file
berghei_counts <- read_xlsx('Manuscript_Frontiers_berghei_counts.xlsx')

@@

apply(berghei_tpm[-1], 2, sum)

#Get a list of df for each experiment.

>>>>

---
title: "P.berghei pir analysis"
author: "Timothy Little"
date: "31/08/2021"
output: 
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = TRUE, message = FALSE, warning = FALSE)
options(scipen = 999) # Means that numbers are displayed normally not as 1e6 (1000000)
```

@@

```{r read_files_calc_TPM}
#Reading in the counts from file
berghei_counts <- read.csv('tl20-05_berghei_counts.csv',
                               row.names = 1)

@@

apply(berghei_tpm[-1], 2, sum)
```

```{r save_tpm_oldNames_allSamples}
#Save the 'raw' TPM before any samples have been removed or sample names combined.

write.csv()

```{r expt_tpms}
#Get a list of df for each experiment.
